Adopting agile in the large: motivations, success factors and challenges

### 2014-05-08 journal/article.tex
Challenge: Previous organization in silos

>>>>

% Challenge: Previous organization in silos is haunting new model
% Is this good??

In some cases problems were caused by internal boundaries or silos in the
initial organization. Cloke [P10] describes how use of Scrum revealed an
internal segmentation where teams operated with differing priorities and
agendas. This segmentation also hampered the initial effort to use Scrum in a
larger context [P10].
Projects needed specialized skills that were scarce and people were often
relocated to match the needs of the moment, but too much reorganization made
it diffucult for teams to plan ahead [P11].
A dispersed matrix organization causes also problems when people are on one hand
kept assigned to many projects simultaneously, but on the other hand functions
such as database administration, architecture boards, and project management are
centralized [P14].
